First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei

### 2017-05-09 eg6-letters/coherent/dvcs_he4_prl.tex
Implement comments from BR and VB

%
\date{\today}
\begin{abstract}
We report the first fully exclusive measurement of coherent deeply virtual 
Compton scattering off a nucleus for $A>1$. The experiment used the 6 GeV 
electron beam from the CEBAF accelerator at Jefferson Lab incident on a $^4$He gas 
target in the center of the CEBAF large acceptance spectrometer (CLAS). A new radial 
time projection chamber (RTPC) was used to detect the recoiling $^4$He
nuclei and ensure the exclusivity of the process. The measured beam-spin 
asymmetries are larger than that observed on the proton in the same kinematic 
domain. Since $^4$He is a spin-zero target, we were able to extract, in a 
completely model-independent way, the real and imaginary parts of the $^4$He 
Compton form factors, $\cal H_A$, which are functions of the generalized parton 
distribution $H_A$. This pioneering measurement of coherent deeply virtual 
Compton scattering on the $^4$He nucleus, with a fully exclusive final state 
via nuclear recoil tagging, leads the way toward 3D imaging of the partonic 
structure of nuclei.
\end{abstract}
\pacs{Valid PACS appear here}

@@

The most promising way to access GPDs experimentally is through the measurement 
of deeply virtual Compton scattering (DVCS), \textit{i.e.}, the hard exclusive 
electroproduction of a real photon.  While other processes are known to be 
sensitive to GPDs, the measurement of DVCS is considered the cleanest probe and 
has been the focus of worldwide efforts 
\cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema} 
involving several accelerator facilities such as Jefferson Lab, HERA, and CERN.  
The vast majority of these measurements focused on the study of proton 
structure and allowed for an extraction of the three-dimensional picture of the 
nucleon (for details on the formalism, see 
\cite{Goeke:2001tz,Diehl:2003ny,Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}).
This framework is also applicable to nuclei, giving access to completely new 
information about nuclear structure in terms of quarks and 
gluons \cite{Dupre:2015jha}.
Study of the 3D structure of nuclei appears to be especially important
in light of the large nuclear effects observed in nuclear parton distribution 
functions \cite{Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}.

\begin{figure}[tb]
\includegraphics[width=6.5cm]{figs/DVCS_diagram.pdf}
\caption{Representation of the leading order handbag diagram of the DVCS 
process off $^4$He.}
\label{fig:diags}
\end{figure}

One must overcome two major experimental challenges in measuring coherent 
nuclear DVCS, $eA\rightarrow e^\prime A^\prime\gamma$. First, the cross section 
of coherent scattering is suppressed due to the nuclear form factor, and 
second, the intact recoil nucleus ($A^\prime$) must be detected to ensure coherence.  
Figure \ref{fig:diags} illustrates the handbag diagram for coherent DVCS on 
$^4$He, where four-vectors of the electrons, photons, and $^4$He are denoted by
$k/k^\prime$, $q/q^\prime$, and $p/p^\prime$ respectively. For large virtual photon's 
4-momentum squared, $Q^2=-(k-k')^{2}$, and small squared momentum transfer, $t=(p-p')^{2}$, the DVCS handbag 
diagram can be factorized into two parts \cite{Freund_Collins,Ji_Osborne}. The 
hard part includes the photon-quark interaction and is calculable in 
perturbative QCD. The non-perturbative part is parametrized in terms of GPDs, 
which embed the partonic structure of the hadron. The GPDs depend on the three 
variables $x$, $\xi$, and $t$ as introduced in Fig.~\ref{fig:diags}. The 
parameter $\xi$ relates to the Bjorken variable $x_{B}$: $\xi\approx 
{{x_B}\over{2-x_B}}$, where $x_B=\frac{Q^2}{2M\nu}$, $\nu=k^0-k^{0\prime}$, and 
$M$ is the proton mass. The parameter $x$ is the quark's internal loop momentum 
fraction and cannot be accessed experimentally. We in fact measure 
Compton form factors (CFF) \cite{Guidal:2013rya}, which are
complex amplitudes defined as:

@@

The CEBAF large acceptance spectrometer in Hall-B at Jefferson Lab has been
previously used successfully for DVCS measurements on the nucleon
\cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}.  In order
to extend its capabilities to nuclear DVCS with a fully exclusive final state,
we built a specialized radial time projection chamber (RTPC) for the detection
and identification of low-energy recoiling light nuclei. 
The experiment E08-024 took place in Hall-B at Jefferson Lab in 2009 using the 
nearly 100\% duty factor, longitudinally polarized electron beam (83$\%$ 
polarization) at an energy of 6.064 GeV. The data were collected over 40 days 
using a 6 atm gaseous $^4$He target placed 64 cm upstream of the nominal center 
of CLAS. For DVCS experiments, the CLAS baseline design \cite{Mecking:2003zu} 
is supplemented with an inner calorimeter (IC) and a solenoid magnet. The IC 
extends the photon detection acceptance of CLAS to polar angles as low as 
4$^{\circ}$. The low-energy M\o{}ller electrons produced in the target form a 
very high rate background that is suppressed by a 5-Tesla solenoid magnet 
placed around the target.

In our kinematics, the recoil $^4$He nuclei produced in DVCS have low momentum,
averaging 300 MeV/c. CLAS cannot detect such low energy $\alpha$ 
particles, so in order to ensure the exclusivity of the measurement, we built a 
small and light RTPC to complement CLAS. The RTPC is a $20$-cm-long cylinder 
with a diameter of $15$ cm, positioned directly around the $^4$He gaseous 
target. The target is a $25$-cm-long and $6$-mm-diameter Kapton straw with 
$27$-$\mu$m-thick walls. The RTPC was calibrated specifically for the detection of 
$^4$He nuclei by utilizing elastic scattering $e^4$He$\to e^\prime$$^4$He with
a 1.2~GeV electron beam.

@@

%DVCS selection
To identify coherent DVCS events, we first select events where one electron, 
one $^4$He, and at least one photon are detected in the final state. Electrons 
are identified using their measured momentum, time, and energy obtained from 
the CLAS drift chambers, Cerenkov counters, scintillator counters, 
and electromagnetic calorimeters. The recoiling $^4$He nuclei are identified in 
the RTPC using time, track quality, and energy-loss cuts for tracks in the 
fiducial region \cite{Hattawy:thesis}. In addition, we apply a vertex-matching cut to ensure that the 
electron and helium nucleus originate from a common reaction vertex in the target cell. The photons are 
detected in either the IC or the CLAS electromagnetic calorimeter. Note that 
even though the DVCS reaction has only one real photon in the final state, 
events with more than one good photon are not discarded at this stage. Indeed,
soft photons are produced at very high rates by the electron beam and create 
numerous accidental coincidences. These do not affect directly our mesurement, 
where only the most energetic photon is considered as DVCS photon candidate.
This prescription however slightly increases the corrections associated with
the $\pi^0$ and the accidental backgrounds discussed below.

To ensure the interaction occurs at the partonic level and the DVCS handbag 
diagram is dominant, we select events with $Q^{2}$ greater than 1 
GeV$^{2}/$c$^{2}$. Exclusivity of the coherent DVCS reaction is optimized by 
applying a set of cuts on the following kinematic variables: the coplanarity 
angle ($\Delta\phi$) between the ($\gamma,\gamma^*$) 
and ($\gamma^*$,$^4$He$'$) planes, the missing energy, mass, and transverse
momentum of the $e'^4$He$'\gamma$ system, the missing mass squared of the $e'^4$He$'$ system, and the angle ($\theta$) 
between the measured photon and the missing momentum of the $e'^4$He$'$ system.  
The experimental data for the most relevant exclusivity observables and applied
cuts is shown in Fig.~\ref{fig:kin-cuts} (see \cite{Hattawy:thesis} for additional details).
%The most relevant of these cuts are presented in Fig.~\ref{fig:kin-cuts}, which 
%shows 3$\sigma$ cuts except for the missing energy (which appears to be too 
%large and for which we reduced the cut window to [-0.45,0.5] GeV).
We also 
reject events where a $\pi^0$ is identified by invariant mass reconstruction of 
two photons. About 3200 events pass these requirements, and their kinematic 
distributions are shown in Fig.~\ref{fig:kin-coverage}.

\begin{figure}[tb]
\includegraphics[width=9cm]{figs/coh_exc_cuts.pdf}
\caption{Four of the six coherent DVCS exclusivity cuts. The black 
distributions represent the initial candidate events, while the shaded 
distributions represent those which which passed all the exclusivity cuts except 
the quantity plotted. The vertical red lines represent the applied cuts.
The distributions from left to right and from top to bottom are: $\Delta 
\phi$, missing energy, missing mass squared and the cone angle ($\theta$) 
between the measured and the calculated photon.}
\label{fig:kin-cuts}
\end{figure}

\begin{figure}[tb]
\hspace{-0.45cm}
\includegraphics[width=8.5cm]{figs/Q2_xB_t_Coh.pdf}
\caption{Coherent DVCS event distributions for $Q^{2}$ as a function of 
$x_{B}$ (left) and $Q^{2}$ as a function of $-t$ (right) after the 
exclusivity cuts.}
\label{fig:kin-coverage}
\end{figure}

@@

The DVCS and well-known Bethe-Heitler (BH) processes, in which the real 
photon is emitted by the incoming or the outgoing lepton, have the same final 
state and are indistinguishable. The amplitude of electroproduction of real
photons includes a sum of the amplitudes of these two processes. The BH 
amplitude is defined by the target form factors, while the DVCS amplitude is 
a combination of the form factors and GPDs. For our kinematics, the cross 
section of real photon electroproduction is dominated by the BH 
contribution, while the DVCS contribution is very small. Its effect is however
enhanced in the observables sensitive to the interference term, {\it e.g.} 
BSA. The three terms entering the cross section calculation,
the square of the BH and DVCS amplitudes and their interference term, depend on the
azimuthal angle $\phi$ between the $(e,e^\prime)$ and $(\gamma^*,^4$He$^\prime)$ planes,
as shown for the nucleon in Ref.~\cite{Belitsky:2001ns} and for the spin-zero targets
in Refs.~\cite{Kirchner:2003wt,Belitsky:2008bz}. Based on this work, the BSA 
of a spin-zero hadron can be expressed as
\begin{equation}
\begin{split}
&A_{LU}(\phi) = \\
&\frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( \Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)},
\end{split}
\label{eq:A_LU-coh}
\end{equation}
where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
and real parts of the $^4$He CFF $\mathcal{H}_{A}$ and depend on the GPD $H_A$.  
Explicit expressions of the purely kinematic factors $\alpha_i$ are written in
Ref.~\cite{Belitsky:2008bz} and are functions of Fourier harmonics in the 
azimuthal angle $\phi$, the nuclear form factor $F_A(t)$, $Q^2$, $x_B$,
$x_{A} = \frac{x_{B}M_{N}}{M_{A}}$, $y=\frac{Q^{2}}{2x_{A}M_{A}E_{beam}}$, and 
$\epsilon = \frac{2x_{A}M_{A}}{\sqrt{Q^{2}}}$, where $M_{A}$($M_{N}$) is the $^4$He 
(nucleon) mass. Using the different $\sin(\phi)$ and $\cos(\phi)$ contributions 
in these factors, it is possible to unequivocally extract both imaginary and real 
parts of $\mathcal{H}_{A}$ by fitting the $A_{LU}(\phi)$ distrubution.

In this work, the azimuthal dependence of the beam-spin asymmetry has been studied 
for a wide range of kinematics ($Q^2$ between 1 and 2.2 GeV$^2$/c$^2$, $x_B$ between
0.1 and 0.3, and $-t$ between 0.07 and 0.16 GeV$^2$/c$^2$). We identified two main
backgrounds to our measurement, accidental coincidences and exclusive coherent
$\pi^0$ production.  The accidentals have particles originating from different events,
and we estimated their contribution to be 4.1\% of our sample. We evaluated this 
contribution by selecting events passing all our cuts but with an electron and 
helium originating from different vertices. The $\pi^0$ production can easily
be mistaken for DVCS when one of the two photons from the $\pi^0$ 
decay is produced at low energy in the laboratory frame and remains undetected.  
To estimate the effect of this background, we developed an event generator 
tuned on the experimental yield of exclusive $\pi^0$ measured by our 
experiment. We used this generator together with a GEANT3 simulation of our 
detector to estimate the ratio of the number of $\pi^0$ events where the 
two photons are detected to those that are misidentified as DVCS events. This 
ratio is then multiplied by the measured yield of exclusive $\pi^0$ events to 
correct the DVCS data.  Depending on the kinematics, we found contaminations of 
2 to 4\%.  Studies of systematic uncertainties showed that the main 
contributions come from the choice of DVCS exclusivity cuts (8\%) and the 
large binning size (5.1\%), where the values are relative and quoted for $A_{LU}$
at $\phi=90^\circ$.  Added quadratically, the total systematic uncertainty
is about 10\% at $90^\circ$ (or 0.03, absolute), which is significantly smaller
than the statistical uncertainties in all kinematical bins.

Due to limited statistics, dependence of the extracted asymmetries on the kinematical variables $Q^2$, 
$x_B$, and $t$ has been studied separately. In Fig.~\ref{fig:alu}, $A_{LU}$ for 
bins in each of the three variables is presented. The curves on the plots are fits with 
the function presented in Eq.~(\ref{eq:A_LU-coh}), where the real and imaginary 
parts of the CFF $\mathcal{H}_{A}$ are the free parameters of the fit.  In 
Fig.~\ref{fig:alu90} the $Q^2$, $x_{B}$, and $t$-dependencies of the fitted 
$A_{LU}$ at $\phi$~=~90$^{\circ}$ are shown. The $x_{B}$ and $t$-dependencies 
are compared to theoretical calculations performed by S.~Liuti and K.~Taneja 
\cite{simonetta_2}. The model accounts for the effect on the quark 
distribution of the virtuality (off-shellness) of the nucleon. The calculations are at slightly 
different kinematics than our data but still provide some guidance. The 
experimental results appear to have a larger asymmetries than the calculations. 
The difference may arise from the theoretical uncertainty in the determination 
of the crossing point where the parton nuclear distribution becomes larger than the 
nucleon one, and reverses the sign of the nuclear effect.

\begin{figure}[tb]
\includegraphics[width=8cm]{figs/coherent-ALU.pdf}
\caption{The coherent $A_{LU}$ as a function of $\phi$. Results are presented
   for different $Q^{2}$ bins (top panel), $x_{B}$ bins (middle panel), and $t$ 
   bins (bottom panel).  The error bars represent the statistical 
   uncertainties. The gray bands represent the systematic uncertainties, 
   including the normalisation uncertainties. The red curves are the results of 
our fits with the form of equation \ref{eq:A_LU-coh}.}
\label{fig:alu}
\end{figure}

@@

The $Q^2$, $x_B$, and $t$ dependencies of the $^4$He CFF $\mathcal{H}_A$ 
extracted from the fit to the azimuthal dependence of $A_{LU}$ are shown in 
Fig.~\ref{fig:CFF_HA}. Curves on the graphs are model calculations, labelled 
{\it convolution} and {\it off-shell}. In the convolution model 
\cite{Vadim_priv}, the nucleus is assumed to be composed of non-relativistic 
nucleons, each interacting independently with the probe. The Convolution-Dual 
model is based on nucleon GPDs from the dual parametrization 
\cite{Guzey:2006xi}, where the Convolution-VGG uses nucleon GPDs  from the VGG 
model and is based on the double distributions ansatz \cite{DD_model}. The 
off-shell model is the same as in Figure \ref{fig:alu90} using an improved
GPD model for the nucleon \cite{GonzalezHernandez:2012jv}.

The results in Fig.~\ref{fig:CFF_HA} show that the extraction of the CFF
from the BSA is possible without any model dependent 
assumptions. The amplitude and the dependencies observed as a function of 
$Q^{2}$, $x_B$, and $t$ are in agreement with the theoretical expectations. One 
can see a difference between the precision of the extracted imaginary and real 
parts, which is expected from
Eq.~(\ref{eq:A_LU-coh}) because $\alpha_2$ is much smaller than $\alpha_1$. While the 
accuracy of our results does not allow to discriminate between the models, they 
demonstrate possibility of extraction of the CFF of spin 0 target in a model 
independent way.

>>>>

%
\date{\today}
\begin{abstract}
We report the first exclusive measurement of coherent deeply virtual 
Compton scattering off a nucleus for $A>1$. The experiment used the 6 GeV 
electron beam from the CEBAF accelerator at Jefferson Lab incident on a 
$^4$He gas target in the center of the CEBAF large acceptance spectrometer 
(CLAS). A specially designed radial 
time projection chamber (RTPC) was used to detect the recoiling $^4$He
nuclei and ensure the exclusivity of the process. The measured beam-spin 
asymmetries are larger than that observed on the proton in the same kinematic 
domain. Since $^4$He is a spin-zero target, we were able to extract, in a 
model-independent way, the real and imaginary parts of the $^4$He 
Compton form factors, $\cal H_A$, which are functions of the generalized parton 
distribution $H_A$. This pioneering measurement of coherent deeply virtual 
Compton scattering on the $^4$He nucleus, with a fully exclusive final state 
via nuclear recoil tagging, leads the way toward 3D imaging of the partonic 
structure of nuclei.
\end{abstract}
\pacs{Valid PACS appear here}

@@

The most promising way to access GPDs experimentally is through the measurement 
of deeply virtual Compton scattering (DVCS), \textit{i.e.}, the hard exclusive 
electroproduction of a real photon.  While other processes are known to be 
sensitive to GPDs, the measurement of DVCS is considered the cleanest probe and 
has been the focus of efforts at Jefferson Lab, HERA, and CERN
\cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}.  
The vast majority of these measurements focused on the study of proton 
structure and allowed for an extraction of the three-dimensional image of the 
proton (for details on the formalism, see 
\cite{Goeke:2001tz,Diehl:2003ny,Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}).
This framework is also applicable to nuclei, giving access to novel 
information about nuclear structure in terms of quarks and 
gluons \cite{Dupre:2015jha}.
Study of the 3D structure of nuclei appears to be especially important
in light of the large nuclear effects observed in nuclear parton distribution 
functions \cite{Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}.

\begin{figure}[tb]
\includegraphics[width=6.5cm]{figs/DVCS_diagram.pdf}
\caption{Representation of the leading-order handbag diagram of the DVCS 
process off $^4$He.}
\label{fig:diags}
\end{figure}

One must overcome two major experimental challenges in measuring coherent 
nuclear DVCS, $eA\rightarrow e^\prime A^\prime\gamma$. First, the cross section 
of coherent scattering is suppressed due to the nuclear form factor, and 
second, the intact recoil nucleus ($A^\prime$) must be detected to ensure coherence.  
Fig.~\ref{fig:diags} illustrates the handbag diagram for coherent DVCS on 
$^4$He, where four-vectors of the electrons, photons, and $^4$He are denoted by
$k/k^\prime$, $q/q^\prime$, and $p/p^\prime$ respectively. For large virtual photon's 
4-momentum squared, $Q^2=-(k-k')^{2}$, and small squared momentum transfer, $t=(p-p')^{2}$, the DVCS handbag 
diagram can be factorized into two parts \cite{Freund_Collins,Ji_Osborne}. The 
hard part includes the photon-quark interaction and is calculable in 
perturbative QCD. The non-perturbative part is parametrized in terms of GPDs, 
which embed the partonic structure of the hadron. The GPDs depend on the three 
variables $x$, $\xi$, and $t$ as introduced in Fig.~\ref{fig:diags}. The 
parameter $\xi$ relates to the Bjorken variable $x_{B}$: $\xi\approx 
{{x_B}\over{2-x_B}}$, where $x_B=\frac{Q^2}{2M\nu}$, $\nu=k^0-k^{0\prime}$, and 
$M$ is the proton mass. The parameter $x$ is the quark's internal loop momentum 
fraction and cannot be accessed experimentally. We in fact measure 
Compton form factors (CFF) \cite{Guidal:2013rya}, which are
complex amplitudes defined as:

@@

The CEBAF large acceptance spectrometer (CLAS) in Hall-B at Jefferson Lab has been
previously used successfully for DVCS measurements on the nucleon
\cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}.  In order
to extend its capabilities to nuclear DVCS with a fully exclusive final state,
we built a specialized radial time projection chamber (RTPC) for the detection
and identification of low-energy recoiling light nuclei. 
The experiment E08-024 took place in Hall-B at Jefferson Lab in 2009 using the 
nearly 100\% duty factor, longitudinally polarized electron beam (83$\%$ 
polarization) at an energy of 6.064 GeV. The data were collected over 40 days 
using a 6 atm gaseous $^4$He target placed 64 cm upstream of the nominal center 
of CLAS. For DVCS experiments, the CLAS 
baseline design~\cite{Mecking:2003zu} 
is supplemented with an inner calorimeter (IC) and a solenoid magnet. The IC 
extends the photon detection acceptance of CLAS to polar angles as low as 
4$^{\circ}$. The 5 T solenoid magnet has two functions; it provides the magnetic 
field for the momentum analysis in the RTPC, and at the same time acts as 
the guiding field for the low-energy M\o{}ller electrons, that are absorbed in a  
heavy shield placed around the beam line.

In our kinematics, the recoil $^4$He nuclei produced in DVCS have low momentum,
averaging 300 MeV/c. CLAS cannot detect such low-energy $\alpha$ 
particles, so in order to ensure the exclusivity of the measurement, we built a 
small and light RTPC to complement CLAS. The RTPC is a $20$-cm-long cylinder 
with a diameter of $15$ cm, positioned directly around the $^4$He gaseous 
target. The target is a $25$-cm-long and $6$-mm-diameter Kapton tube with 
$27$-$\mu$m-thick walls. The RTPC was calibrated specifically for the detection of 
$^4$He nuclei by utilizing elastic scattering $e^4$He$\to e^\prime$$^4$He with
a 1.2~GeV electron beam.

@@

%DVCS selection
To identify coherent DVCS events, we first select events where one electron, 
one $^4$He, and at least one photon are detected in the final state. Electrons 
are identified using their measured momentum, time, and energy obtained from 
the CLAS drift chambers, \^{C}erenkov counters, scintillator counters, 
and electromagnetic calorimeters. The recoiling $^4$He nuclei are identified in 
the RTPC using time, track quality, and energy-loss cuts for tracks in the 
fiducial region \cite{Hattawy:thesis}. In addition, we apply a vertex-matching 
cut to ensure that the 
electron and helium nucleus originate from a common reaction vertex in the 
target cell. The photons are 
detected in either the IC or the CLAS electromagnetic calorimeter. Note that 
even though the DVCS reaction has only one real photon in the final state, 
events with more than one good photon are not discarded at this stage. These
are caused by accidental coincidences of soft photons that do not affect 
directly our measurement. We consider only the most energetic photon of an 
event as a DVCS photon candidate.
This prescription however slightly increases the corrections associated with
the $\pi^0$ and the accidental backgrounds discussed below.

To ensure the interaction occurs at the partonic level and the DVCS handbag 
diagram is dominant, we select events with $Q^{2}$ greater than 1 
GeV$^{2}/$c$^{2}$. Exclusivity of the coherent DVCS reaction is optimized by 
applying a set of cuts on the following kinematic variables: the coplanarity 
angle $\Delta\phi$ between the ($\gamma,\gamma^*$) 
and ($\gamma^*$,$^4$He$'$) planes, the missing energy, mass, and transverse
momentum of the $e'^4$He$'\gamma$ system, the missing mass squared of 
the $e'^4$He$'$ system, and the angle $\theta$
between the measured photon and the missing momentum of the $e'^4$He$'$ system.  
The experimental data for the most relevant exclusivity observables and applied
cuts are shown in Fig.~\ref{fig:kin-cuts} (see \cite{Hattawy:thesis} for additional details).
%The most relevant of these cuts are presented in Fig.~\ref{fig:kin-cuts}, which 
%shows 3$\sigma$ cuts except for the missing energy (which appears to be too 
%large and for which we reduced the cut window to [-0.45,0.5] GeV).
We also 
reject events where a $\pi^0$ is identified by invariant mass reconstruction of 
two photons. About 3200 events pass these requirements, and their kinematic 
distributions are shown in Fig.~\ref{fig:kin-coverage}.

\begin{figure}[tb]
\includegraphics[width=9cm]{figs/coh_exc_cuts.pdf}
\caption{Four of the six coherent DVCS exclusivity cuts. The black 
distributions represent the initial candidate events, while the shaded 
distributions represent those which which passed all the exclusivity cuts except 
the quantity plotted. The vertical red lines represent the applied cuts.
The distributions from left to right and from top to bottom are: coplanarity 
angle $\Delta \phi$, missing energy $E_X$, missing-mass-squared $M_X^2$, and 
the cone angle $\theta$ between the measured photon and the missing momentum 
of the $e^\prime$He$^\prime$ system.}
\label{fig:kin-cuts}
\end{figure}

\begin{figure}[tb]
\hspace{-0.45cm}
\includegraphics[width=8.5cm]{figs/Q2_xB_t_Coh.pdf}
\caption{Coherent DVCS event distributions for $Q^2$ after exclusivity cuts. 
The distributions are shown as a function of Bjorken variable $x_B$ (left) 
and as a function of squared-momentum transfer $-t$ (right).}
\label{fig:kin-coverage}
\end{figure}

@@

The DVCS and well-known Bethe-Heitler (BH) processes, in which the real 
photon is emitted by the incoming or the outgoing lepton, have the same final 
state and are indistinguishable. The amplitude of electroproduction of real
photons includes a sum of the amplitudes of these two processes. The BH 
amplitude is defined by the target form factors, while the DVCS amplitude is 
a combination of the form factors and GPDs. For our kinematics, the cross 
section of real photon electroproduction is dominated by the BH 
contribution, while the DVCS contribution is very small. However, the DVCS contribution is
enhanced in the observables sensitive to the interference term, {\it e.g.} 
BSA. The three terms entering the cross section calculation,
the square of the BH and DVCS amplitudes and their interference term, depend on the
azimuthal angle $\phi$ between the $(e,e^\prime)$ and $(\gamma^*,^4$He$^\prime)$ planes,
as shown for the nucleon in Ref.~\cite{Belitsky:2001ns} and for the spin-zero targets
in Refs.~\cite{Kirchner:2003wt,Belitsky:2008bz}. Based on this work, the BSA 
of a spin-zero hadron can be expressed as
\begin{equation}
\begin{split}
&A_{LU}(\phi) = \\
&\frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( \Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)},
\end{split}
\label{eq:A_LU-coh}
\end{equation}
where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
and real parts of the $^4$He CFF $\mathcal{H}_{A}$ and depend on the GPD $H_A$.  
Explicit expressions of the purely kinematic factors $\alpha_i$ are written in
Ref.~\cite{Belitsky:2008bz} and are functions of Fourier harmonics in the 
azimuthal angle $\phi$, the nuclear form factor $F_A(t)$, $Q^2$, $x_B$,
$x_{A} = \frac{x_{B}M_{N}}{M_{A}}$, $y=\frac{Q^{2}}{2x_{A}M_{A}E_{beam}}$, and 
$\epsilon = \frac{2x_{A}M_{A}}{\sqrt{Q^{2}}}$, where $M_{A}$($M_{N}$) is the $^4$He 
(nucleon) mass. Using the different $\sin(\phi)$ and $\cos(\phi)$ contributions, 
both imaginary and real parts of $\mathcal{H}_{A}$ can be extracted unambiguously
by fitting the $A_{LU}(\phi)$ distribution.

In this work, the azimuthal dependence of the beam-spin asymmetry has been studied 
for a wide range of kinematics ($Q^2$ between 1 and 2.2 GeV$^2$/c$^2$, $x_B$ between
0.1 and 0.3, and $-t$ between 0.07 and 0.16 GeV$^2$/c$^2$). We identified two main
backgrounds to our measurement, accidental coincidences and exclusive coherent
$\pi^0$ production.  The accidentals have particles originating from different events,
and we estimated their contribution to be 4.1\% of our sample. We evaluated this 
contribution by selecting events passing all our cuts but with an electron and 
helium originating from different vertices. The $\pi^0$ production can easily
be mistaken for DVCS when one of the two photons from the $\pi^0$ 
decay is produced at low energy in the laboratory frame and remains undetected.  
To estimate the effect of this background, we developed an event generator 
tuned on the experimental yield of exclusive $\pi^0$ measured by our 
experiment. We used this generator together with a GEANT3 simulation of our 
detector to estimate the ratio of the number of $\pi^0$ events where the 
two photons are detected to those that are misidentified as DVCS events. This 
ratio is then multiplied by the measured yield of exclusive $\pi^0$ events to 
correct the DVCS data.  Depending on the kinematics, we found contaminations of 
2 to 4\%. Studies of systematic uncertainties showed that the main contributions 
come from the choice of DVCS exclusivity cuts (8\% systematic uncertainty) and the 
large binning size (5.1\%), where the values are relative and quoted for $A_{LU}$
at $\phi=90^\circ$.  Added quadratically, the total systematic uncertainty
is about 10\% at $90^\circ$ (or 0.03, absolute), which is significantly smaller
than the statistical uncertainties in all kinematical bins.

Due to limited statistics, dependence of the extracted asymmetries on the kinematical variables $Q^2$, 
$x_B$, and $t$ has been studied separately. In Fig.~\ref{fig:alu}, $A_{LU}$ for 
bins in each of the three variables is presented. The curves on the plots are fits with 
the function presented in Eq.~(\ref{eq:A_LU-coh}), where the real and imaginary 
parts of the CFF $\mathcal{H}_{A}$ are the free parameters of the fit.  In 
Fig.~\ref{fig:alu90} the $Q^2$, $x_{B}$, and $t$-dependencies of the fitted 
$A_{LU}$ at $\phi$~=~90$^{\circ}$ are shown. The $x_{B}$ and $t$-dependencies 
are compared to theoretical calculations by S.~Liuti and K.~Taneja 
\cite{simonetta_2}. The model accounts for the effect on the quark 
distribution of the virtuality (off-shellness) of the nucleon. The calculations are at slightly 
different kinematics than our data but still allow drawing some conclusions. The 
experimental results appear to have a larger asymmetries than the calculations. 
The difference may arise from the theoretical uncertainty in the determination 
of the crossing point where the parton nuclear distribution becomes larger than the 
nucleon one, and reverses the sign of the nuclear effect.

\begin{figure}[tb]
\includegraphics[width=8cm]{figs/coherent-ALU.pdf}
\caption{The coherent $A_{LU}$ as a function of azimuthal angle $\phi$. Results are presented
   for different $Q^{2}$ bins (top panel), $x_{B}$ bins (middle panel), and $t$ 
   bins (bottom panel).  The error bars represent the statistical 
   uncertainties. The gray bands represent the systematic uncertainties, 
   including the normalisation uncertainties. The red curves are the results of 
our fits with the form of equation \ref{eq:A_LU-coh}.}
\label{fig:alu}
\end{figure}

@@

The $Q^2$, $x_B$, and $t$ dependencies of the $^4$He CFF $\mathcal{H}_A$ 
extracted from the fit to the azimuthal dependence of $A_{LU}$ are shown in 
Fig.~\ref{fig:CFF_HA}. Curves on the graphs are model calculations, labelled 
{\it convolution} and {\it off-shell}. In the convolution model 
\cite{Vadim_priv}, the nucleus is assumed to be composed of non-relativistic 
nucleons, each interacting independently with the probe. The Convolution-Dual 
model is based on nucleon GPDs from the dual parametrization 
\cite{Guzey:2006xi}, where the Convolution-VGG uses nucleon GPDs  from the VGG 
model and is based on the double distributions ansatz \cite{DD_model}. The 
off-shell model is the same as in Fig.~\ref{fig:alu90} using an improved
GPD model for the nucleon \cite{GonzalezHernandez:2012jv}.

The results in Fig.~\ref{fig:CFF_HA} show that the extraction of the CFF
from the BSA is possible without any model dependent 
assumptions. The amplitude and the dependencies observed as a function of 
$Q^{2}$, $x_B$, and $t$ are in agreement with the theoretical expectations. One 
can see a difference between the precision of the extracted imaginary and real 
parts, this result is expected because of Eq.~(\ref{eq:A_LU-coh}) where 
$\alpha_2$ is much smaller than $\alpha_1$. While the precision of this 
measurement is not at a sufficient level to discriminate between the models, 
these results demonstrate the possibility of extracting the CFF of a spin 0 
target in a model independent way directly from a BSA measurement.
